---
title: 'Type I Error Control'
author: "Alessia Buratin"
date: 'Compiled: `r format(Sys.Date(), "%d %B, %Y")`'
output:
  html_document:
    code_folding: hide
    df_print: kable
    number_sections: no
    theme: united
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
editor_options: 
  chunk_output_type: console
---

<style>
#TOC {
  top: 1%;
  opacity: 0.5;
}
#TOC:hover {
  opacity: 1;
}
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data loading

```{r}
library(reshape2)
library(ggplot2)
library(cowplot)
library(plyr)
```

Choose samples in completely random way and create two groups of equal sample size.

### ALZ Data - Mock datasets

```{r}
## load meta data
meta.data <- read.csv("/blackhole/alessia/GLMM_article/data/meta_alz.csv")
meta.data

coldata <- DataFrame(condition = meta.data$condition,
                     group = meta.data$group,
                     sample = meta.data$sample,
                     row.names = meta.data$sample)
coldata$condition <- factor(coldata$condition)
coldata$group <- factor(coldata$group)
coldata$sample <- as.character(coldata$sample)
coldata

```

# Differential expression tests

Use "glm_glmm_paired.R" for GLMM-ZINB model and GLM-NB model to evaluate mock datasets. An output is generated for each evaluation. 

```{r}

load(file = "/blackhole/alessia/GLMM_article/type_I_error_control/ALZ_GLM_30rep.RData")
load(file = "/blackhole/alessia/GLMM_article/type_I_error_control/ALZ_typeIerror_GLMM_30rep.RData")
rate = rbind.fill(ratemodel.dt,
                  rbindlist(rateGLMM_tIe, idcol="rep"))
colnames(rate) = c("alpha","Rep","Method","rate")
rate_df = as.data.frame(rate)

```

# Plot

```{r}
library(RColorBrewer)
cols <- c(
  # GLMM
  brewer.pal(n = 9, "BuPu")[c(5)],
  
  # DEseq
  brewer.pal(n = 9, "YlOrRd")[c(3)],
  # Edger
  brewer.pal(n = 9, name = "GnBu")[c(5)],
  # limma
  brewer.pal(n = 9, "RdPu")[c(5)]
)

methods2 <- c("GLMM",
              
              "DESeq2",
             
              "edgeR",
              
              "voom")
names(cols) <- methods2
renameAtoB <- function(f,a,b) {
  levels(f)[levels(f) == a] <- b
  f
}
rate_df$Method = factor(rate_df$Method)
rate_df$Method <- renameAtoB(rate_df$Method, "edgeR.robust", "edgeR")

rate_df$alpha = factor(rate_df$alpha)
rate_df$alpha <- renameAtoB(rate_df$alpha, "res.1", "0.1")
rate_df$alpha <- renameAtoB(rate_df$alpha, "res.05", "0.05")

rate_df$Method <- as.character(rate_df$Method)

divergence_FDR_mean_melted <- ddply(.data = rate_df,.variables = ~ Method + alpha,.fun = function(x){
  if(x$alpha == "0.1"){
    sum(abs(x[,"rate"]-0.1))/30
  } else if(x$alpha == "0.05"){
    sum(abs(x[,"rate"]-0.05))/30
  }
})
divergence_FDR_mean_melted$Method = factor(divergence_FDR_mean_melted$Method)
# rank the methods
ranked_divergence_FDR_mean_melted <- ddply(divergence_FDR_mean_melted,.variables = ~ alpha, function(x) rank(x[,"V1"]))
colnames(ranked_divergence_FDR_mean_melted) <- c("alpha",levels(divergence_FDR_mean_melted$Method))
FDR_divergence_summary <- data.frame(method = levels(divergence_FDR_mean_melted$Method), value = apply(ranked_divergence_FDR_mean_melted[,-(1)],2,mean))
saveRDS(object = FDR_divergence_summary,file = "/blackhole/alessia/GLMM_article/data/FDR_divergence_summary_ALZ.RDS")

rate_df_005 = rate_df %>% dplyr::filter(alpha=="0.05")
rate_df_01 = rate_df %>% dplyr::filter(alpha=="0.1")

png(paste0("/blackhole/alessia/GLMM_article/type_I_error_control/TIE_ALZ_30rep.png"), units = "cm", width = 20, height = 20, res = 100)

ggplot(data = pval_df_FDR_mean,aes(color = Method)) +
    geom_boxplot(data = pval_df_FDR_mean001,aes(x = "0.01",y = FDR_obs001)) +
    geom_boxplot(data = pval_df_FDR_mean005,aes(x = "0.05",y = FDR_obs005)) +
    geom_boxplot(data = pval_df_FDR_mean01,aes(x = "0.1",y = FDR_obs01)) + 
    #geom_hline(yintercept = c(0.01,0.05,0.1),lty = 2, color = "darkgray") +
    geom_segment(aes(x = 1-0.5,xend = 1+0.5,y = 0.01,yend = 0.01), color = "red", lty = 2) +
    geom_segment(aes(x = 2-0.5,xend = 2+0.5,y = 0.05,yend = 0.05), color = "red", lty = 2) +
    geom_segment(aes(x = 3-0.5,xend = 3+0.5,y = 0.1,yend = 0.1), color = "red", lty = 2) +
    xlab(expression(Nominal~alpha)) + ylab(expression("Observed"~alpha)) +
    #ggtitle(label = "False discoveries for each method") + 
    scale_color_manual(values = cols) +
    theme_minimal() + 
    ggtitle(label = paste("False discoveries for",tech,"stool samples"),subtitle = "Raw p-values") +
    theme(legend.position = "none")

ggplot(data = rate_df, aes( color = Method)) +
    geom_boxplot(data = rate_df, aes(x = fct_reorder(Method,rate, .desc=FALSE), y = rate)) +
    scale_y_sqrt(expand=c(0,0)) +
    # geom_boxplot(data = pval_df_FDR_mean005,aes(x = "0.05",y = FDR_obs005)) +
    # geom_boxplot(data = pval_df_FDR_mean01,aes(x = "0.1",y = FDR_obs01)) + 
    geom_hline(yintercept = c(0.01, 0.05,0.1), lty = 2, color = "darkred") +
    # geom_segment(aes(x = 1-0.5,xend = 1+0.5,y = 0.1,yend = 0.1), color = "red", lty = 2) +
    # geom_segment(aes(x = 2-0.5,xend = 2+0.5,y = 0.05,yend = 0.05), color = "red", lty = 2) +
    # geom_segment(aes(x = 3-0.5,xend = 3+0.5,y = 0.1,yend = 0.1), color = "red", lty = 2) +

    # xlab(expression(Nominal~alpha)) + 
  xlab("DEMs") + 
  ylab(expression("Observed"~alpha)) +

    #ggtitle(label = "False discoveries for each method") + 
    scale_color_manual(values = cols) +
    theme_classic2() +
      facet_wrap( ~ alpha) + 
    ggtitle(label = expression(Nominal~alpha)) + #paste("False discovery rate for ALZ dataset"),subtitle = "Raw p-values") +
    theme(legend.position = "none",
          axis.text.x = element_text(size=12,angle = 30, hjust = 1),
          axis.text.y = element_text(size = 12),
          axis.title = element_text(size=12),
          # axis.text.y.left = element_text(size = 11),
          title=element_text(size=12),
          strip.text.x = element_text(size = 12))
dev.off()

```


# Plot

```{r}
pval_df_list = list(ALZ = resMethods, TALL = resMethods_TALL)
produce_pval_df <- function(ps_fitted_list){
  pval_df_list <- lapply(X = ps_fitted_list,FUN = function(Comparison){
    ldply(Comparison,function(method){
      data.frame(pval = method$pValMat[,1])
    },.id = "Method")
  }) 
  
  pval_df <- ldply(pval_df_list, .id = "DataSet")
  pval_df$Method <- factor(pval_df$Method,levels = c("DESeq2_poscounts",
                                                     "DESeq2_TMM",
                                                     "DESeq2_poscounts_zinbwave",
                                                     "edgeR_TMM_standard",
                                                     "edgeR_poscounts_standard",
                                                     "edgeR_TMM_robustDisp",
                                                     "edgeR_TMM_zinbwave",
                                                     "limma_voom_TMM",
                                                     "limma_voom_TMM_zinbwave",
                                                     "ALDEx2",
                                                     "mgsZig_CSS",
                                                     "corncob_LRT",
                                                     "corncob_wald",
                                                     "MAST",
                                                     "seurat_wilcoxon",
                                                     "scde"),ordered = TRUE)
  
  pval_df_FDR <- ddply(.data = pval_df,.variables = ~ Comparison + Method,.fun = function(x){
    x$FDR_obs001 <- sum(x$pval<0.01,na.rm = TRUE)/length(x$pval[!is.na(x$pval)])
    x$FDR_obs005 <- sum(x$pval<0.05,na.rm = TRUE)/length(x$pval[!is.na(x$pval)])
    x$FDR_obs01 <- sum(x$pval<0.1,na.rm = TRUE)/length(x$pval[!is.na(x$pval)])
    return(x)
  })
  pval_df_FDR_mean <- ddply(.data = pval_df_FDR,.variables = ~ Comparison + Method,.fun = function(x){
    colMeans(x[,4:6])
  })
  
  # Create data frame for empirical and theoretical p-values
  pval_df_qq <- suppressWarnings(ddply(.data = pval_df,.variables = ~ Comparison + Method,.fun = function(x){
    x <- x[order(x$pval),]
    x$pval_theorical[!is.na(x$pval)] <- (1:(sum(!is.na(x$pval))))/(sum(!is.na(x$pval)))
    x$pval_theorical_rounded[!is.na(x$pval)] <- round((1:(sum(!is.na(x$pval))))/(sum(!is.na(x$pval))),digits = 2)
    x$KS <- ks.test(x = x$pval_theorical[!is.na(x$pval)],y = x$pval[!is.na(x$pval)])$statistic
    x$KS_pval <- ks.test(x = x$pval_theorical[!is.na(x$pval)],y = x$pval[!is.na(x$pval)])$p.value
    #x$KLD <- KLD(x$pval_theorical[!is.na(x$pval)],x$pval[!is.na(x$pval)])$sum.KLD.px.py
    #x$KLD_0.1 <- KLD(x$pval_theorical[!is.na(x$pval) & x$pval_theorical < 0.1],x$pval[!is.na(x$pval) & x$pval_theorical < 0.1])$sum.KLD.px.py
    return(x)
  }))
  
  # For each theoretical p-value, the mean of observed one is computed. 
  pval_df_qq_summary <- ddply(.data = pval_df_qq,.variables = ~ Method + pval_theorical_rounded,.fun = function(x){
    pval_mean <- mean(x$pval)
    return(pval_mean)
  })
  names(pval_df_qq_summary) <- c("Method","pval_theorical","pval_observed")
  
  ### Kolmogorov-Smirnov test
  
  pval_df_KS_summary <- ddply(.data = pval_df_qq,.variables = ~ Comparison + Method,.fun = function(x){
    colMeans(x[,6:7])})
  
  return(list(pval_df = pval_df,
              pval_df_FDR_mean = pval_df_FDR_mean,
              pval_df_qq_summary = pval_df_qq_summary,
              pval_df_KS_summary = pval_df_KS_summary))
}
plot_FDRcheck <- function(dataset,tech){
  pval_df_FDR_mean <- dataset$pval_df_FDR_mean
  
  ord001 <- order(ddply(pval_df_FDR_mean,.variables = ~ Method, function(x) mean(x$FDR_obs001))$V1)
  ord005 <- order(ddply(pval_df_FDR_mean,.variables = ~ Method, function(x) mean(x$FDR_obs005))$V1)
  ord01 <- order(ddply(pval_df_FDR_mean,.variables = ~ Method, function(x) mean(x$FDR_obs01))$V1)
  
  pval_df_FDR_mean001 <- pval_df_FDR_mean
  pval_df_FDR_mean001$Method <- factor(pval_df_FDR_mean$Method, levels = levels(pval_df_FDR_mean$Method)[ord001],ordered = TRUE)
  
  pval_df_FDR_mean005 <- pval_df_FDR_mean
  pval_df_FDR_mean005$Method <- factor(pval_df_FDR_mean$Method, levels = levels(pval_df_FDR_mean$Method)[ord005],ordered = TRUE)
  
  pval_df_FDR_mean01 <- pval_df_FDR_mean
  pval_df_FDR_mean01$Method <- factor(pval_df_FDR_mean$Method, levels = levels(pval_df_FDR_mean$Method)[ord01],ordered = TRUE)
  
  g <- ggplot(data = pval_df_FDR_mean,aes(color = Method)) +
    geom_boxplot(data = pval_df_FDR_mean001,aes(x = "0.01",y = FDR_obs001)) +
    geom_boxplot(data = pval_df_FDR_mean005,aes(x = "0.05",y = FDR_obs005)) +
    geom_boxplot(data = pval_df_FDR_mean01,aes(x = "0.1",y = FDR_obs01)) + 
    #geom_hline(yintercept = c(0.01,0.05,0.1),lty = 2, color = "darkgray") +
    geom_segment(aes(x = 1-0.5,xend = 1+0.5,y = 0.01,yend = 0.01), color = "red", lty = 2) +
    geom_segment(aes(x = 2-0.5,xend = 2+0.5,y = 0.05,yend = 0.05), color = "red", lty = 2) +
    geom_segment(aes(x = 3-0.5,xend = 3+0.5,y = 0.1,yend = 0.1), color = "red", lty = 2) +
    xlab(expression(Nominal~alpha)) + ylab(expression("Observed"~alpha)) +
    #ggtitle(label = "False discoveries for each method") + 
    scale_color_manual(values = cols) +
    theme_minimal() + 
    ggtitle(label = paste("False discoveries for",tech,"stool samples"),subtitle = "Raw p-values") +
    theme(legend.position = "none")
  return(g)
}
plot_qq <- function(dataset,tech,zoom = c(0,1)){
  pval_df_qq_summary <- dataset$pval_df_qq_summary
  
  df_segments <- data.frame(x1 = c(0.01,0,0.05,0,0.1,0),
                            x2 = c(0.01,0.01,0.05,0.05,0.1,0.1),
                            y1 = c(0,0.01,0,0.05,0,0.1),
                            y2 = c(0.01,0.01,0.05,0.05,0.1,0.1))
  
  ggplot(data = pval_df_qq_summary,aes(x = pval_theorical, y = pval_observed, color = Method)) +
    geom_line() +
    #geom_path(aes(group = Comparison)) +
    #facet_wrap(~ Method) +
    geom_abline() +
    coord_cartesian(xlim = zoom,ylim = zoom) +
    xlab("Theoretical p-value") + ylab(paste("Observed p-value")) +
    #xlab("") + ylab(paste("")) +
    scale_color_manual(values = cols) +
    theme_minimal() +
    theme(legend.position = "none") +
    geom_segment(aes(x = x1,xend = x2,y = y1,yend = y2), color = "red", lty = 2,data = df_segments)
}
plot_KS <- function(dataset,tech){
  pval_df_KS_summary <- dataset$pval_df_KS_summary
  ord <- order(ddply(pval_df_KS_summary,.variables = ~ Method, function(x) mean(x$KS))$V1)
  pval_df_KS_summary$Method <- factor(pval_df_KS_summary$Method, levels = levels(pval_df_KS_summary$Method)[ord],ordered = TRUE)
  ggplot(melt(pval_df_KS_summary[,1:3]),aes(x = Method,y = value, color = Method)) +
    geom_boxplot() +
    theme_minimal() +
    #geom_text(aes(label = round(mean(value),digits = 3)),hjust = -0.1) +
    coord_flip() +
    ylab("KS statistics") + xlab("Methods") +
    ggtitle(label = paste("KS statistics -",tech,"stool samples"),subtitle = "Ordered methods") +
    scale_x_discrete(limits = rev(levels(pval_df_KS_summary$Method)),position = "top") +
    scale_color_manual(values = cols) +
    theme(legend.position = "none",
          # axis.text.y = element_blank(),
          panel.spacing = unit(0, "lines"),
          plot.margin = unit(c(0,0,0,1), "cm"))
}
legend_method <- function(dataset, nrow){
  pval_df_KS_summary <- dataset$pval_df_KS_summary
  df_method <- data.frame(Method = unique(pval_df_KS_summary$Method),
                          pos = cumsum(sapply(unique(pval_df_KS_summary$Method),function(x) nchar(as.character(x))+10)))
  g_methods <- ggplot(df_method,aes(x = Method,y = "1", color = Method)) +
    theme_minimal() +
    geom_point(size = 5) +
    scale_color_manual(values = cols, guide = guide_legend(title = "Methods:",nrow = nrow)) +
    theme(legend.position = "bottom")
  return(get_legend(g_methods))
}
```

```{r, fig.height=14, fig.width=16}
if(!file.exists("../data/TIEC_16S_plot.RDS")){
  dataplot_16S <- produce_pval_df(ps_fitted_list = Stool_16S_mockDA,pval_type = "raw")
  saveRDS(dataplot_16S,file = "../data/TIEC_16S_plot.RDS")
} else dataplot_16S <- readRDS("../data/TIEC_16S_plot.RDS")
if(!file.exists("../data/TIEC_WMS_plot.RDS")){
  dataplot_WMS <- produce_pval_df(ps_fitted_list = Stool_WMS_mockDA,pval_type = "raw")
  saveRDS(dataplot_WMS,file = "../data/TIEC_WMS_plot.RDS")
} else dataplot_WMS <- readRDS("../data/TIEC_WMS_plot.RDS")
e <- plot_FDRcheck(dataset = dataplot_16S,tech = "16S")
f <- plot_FDRcheck(dataset = dataplot_WMS,tech = "WMS")
a1 <- plot_qq(dataset = dataplot_16S,tech = "16S",zoom = c(0,1)) + 
  ggtitle(label = paste("QQ-plot 16S stool samples"),subtitle = paste("From 0 to 1"))
a2 <- plot_qq(dataset = dataplot_16S,tech = "16S",zoom = c(0,0.1)) + 
  ggtitle(label = element_blank(),subtitle = paste("From 0 to 0.1"))
a <- plot_grid(plotlist = list(a1,a2),nrow = 2,align = "hv")
c1 <- plot_qq(dataset = dataplot_WMS,tech = "WMS",zoom = c(0,1)) +
  ggtitle(label = paste("QQ-plot WMS stool samples"),subtitle = paste("From 0 to 1"))
c2 <- plot_qq(dataset = dataplot_WMS,tech = "WMS",zoom = c(0,0.1)) + 
  ggtitle(label = element_blank(),subtitle = paste("From 0 to 0.1"))
c <- plot_grid(plotlist = list(c1,c2),nrow = 2,align = "vh")
b <- plot_KS(dataset = dataplot_16S,tech = "16S")
d <- plot_KS(dataset = dataplot_WMS,tech = "WMS")
ab <- plot_grid(plotlist = list(a,b),ncol = 2,axis = "tb",labels = c("a","b"),rel_widths = c(2,3))
abe <- plot_grid(plotlist = list(ab,e),nrow = 2,axis = "lr",labels = c("","e"))
cd <- plot_grid(plotlist = list(c,d),ncol = 2,axis = "tb",labels = c("c","d"),rel_widths = c(2,3))
cdf <- plot_grid(plotlist = list(cd,f),nrow = 2,axis = "lr",labels = c("","f"))
abecdf <- plot_grid(abe,cdf,axis = "tb")
leg <- legend_method(dataset = dataplot_16S, nrow = 3)
fig <- plot_grid(abecdf,leg,nrow = 2,rel_heights = c(1,0.1))
fig
# svg(filename = "../../fig3.svg",width = 16, height = 14)
# fig
# dev.off()
```

# Summary

Average KS statistics and divergence of fraction of false discoveries from nominal values between simulations to rank methods.

```{r, eval=FALSE}
Stool_WMS <- readRDS(file = "../data/Stool_WMS_mockDA.RDS")
Stool_16S <- readRDS(file = "../data/Stool_16S_mockDA.RDS")
### discoveries vs alpha nominal
pVal_df_list_16S <- lapply(X = Stool_16S,FUN = function(Comparison){
  ldply(Comparison,function(method){
    data.frame(pVal = method$pValMat[,1])
  },.id = "Method")
})
pVal_df_list_WMS <- lapply(X = Stool_WMS,FUN = function(Comparison){
  ldply(Comparison,function(method){
    data.frame(pVal = method$pValMat[,1])
  },.id = "Method")
})
pVal_df_16S <- ldply(pVal_df_list_16S,function(x) x, .id = "Comparison")
pVal_df_WMS <- ldply(pVal_df_list_WMS,function(x) x, .id = "Comparison")
pVal_df_16S$technology <- "16S"
pVal_df_WMS$technology <- "WMS"
pVal_df <- rbind(pVal_df_16S,pVal_df_WMS)
pVal_df$Method <- factor(pVal_df$Method,levels = c("DESeq2_poscounts",
                                                   "DESeq2_TMM",
                                                   "DESeq2_poscounts_zinbwave",
                                                   "edgeR_TMM_standard",
                                                   "edgeR_poscounts_standard",
                                                   "edgeR_TMM_robustDisp",
                                                   "edgeR_TMM_zinbwave",
                                                   "limma_voom_TMM",
                                                   "limma_voom_TMM_zinbwave",
                                                   "ALDEx2",
                                                   "mgsZig_CSS",
                                                   "corncob_LRT",
                                                   "corncob_wald",
                                                   "MAST",
                                                   "seurat_wilcoxon",
                                                   "scde"),ordered = TRUE)
# Compute fraction of discoveries
pVal_df_FDR <- ddply(.data = pVal_df,.variables = ~ technology + Comparison + Method,.fun = function(x){
  x$FDR_obs001 <- sum(x$pVal<0.01,na.rm = TRUE)/length(x$pVal[!is.na(x$pVal)])
  x$FDR_obs005 <- sum(x$pVal<0.05,na.rm = TRUE)/length(x$pVal[!is.na(x$pVal)])
  x$FDR_obs01 <- sum(x$pVal<0.1,na.rm = TRUE)/length(x$pVal[!is.na(x$pVal)])
  return(x)
})
# stratified by tech, comparison and method. Compute the mean
pVal_df_FDR_mean <- ddply(.data = pVal_df_FDR,.variables = ~ technology + Comparison + Method,.fun = function(x){
  colMeans(x[,5:7])
})
# melt the dataset and find the difference between fraction and nominal value
pVal_df_FDR_mean_melted <- melt(pVal_df_FDR_mean)
divergence_FDR_mean_melted <- ddply(.data = pVal_df_FDR_mean_melted,.variables = ~ technology + Comparison + Method + variable,.fun = function(x){
  if(x$variable == "FDR_obs001"){
    sum(abs(x[,"value"]-0.01))/1000
  } else if(x$variable == "FDR_obs005"){
    sum(abs(x[,"value"]-0.05))/1000
  } else if(x$variable == "FDR_obs01"){
    sum(abs(x[,"value"]-0.1))/1000
  }
})
# rank the methods
ranked_divergence_FDR_mean_melted <- ddply(divergence_FDR_mean_melted,.variables = ~ technology + Comparison + variable, function(x) rank(x[,"V1"]))
colnames(ranked_divergence_FDR_mean_melted) <- c("technology","Comparison","variable",levels(divergence_FDR_mean_melted$Method))
FDR_divergence_summary <- data.frame(method = levels(divergence_FDR_mean_melted$Method), value = apply(ranked_divergence_FDR_mean_melted[,-(1:3)],2,mean))
saveRDS(object = FDR_divergence_summary,file = "../data/summary/FDR_divergence_summary.RDS")
### KS statistics
# Create a p-value's data frame
pval_df_list_16S <- lapply(X = Stool_16S,FUN = function(Comparison){
  ldply(Comparison,function(method){
    data.frame(pVal = method$pValMat[,1])
  },.id = "Method")
}) 
pval_df_list_WMS <- lapply(X = Stool_WMS,FUN = function(Comparison){
  ldply(Comparison,function(method){
    data.frame(pVal = method$pValMat[,1])
  },.id = "Method")
}) 
# Stratify by Comparison
pval_df_16S <- ldply(pval_df_list_16S,function(x) x, .id = "Comparison")
pval_df_WMS <- ldply(pval_df_list_WMS,function(x) x, .id = "Comparison")
pval_df_16S$technology <- "16S"
pval_df_WMS$technology <- "WMS"
pval_df <- rbind(pval_df_16S,pval_df_WMS)
pval_df$Method <- factor(pval_df$Method,levels = c("DESeq2_poscounts",
                                                   "DESeq2_TMM",
                                                   "DESeq2_poscounts_zinbwave",
                                                   "edgeR_TMM_standard",
                                                   "edgeR_poscounts_standard",
                                                   "edgeR_TMM_robustDisp",
                                                   "edgeR_TMM_zinbwave",
                                                   "limma_voom_TMM",
                                                   "limma_voom_TMM_zinbwave",
                                                   "ALDEx2",
                                                   "mgsZig_CSS",
                                                   "corncob_LRT",
                                                   "corncob_wald",
                                                   "MAST",
                                                   "seurat_wilcoxon",
                                                   "scde"),ordered = TRUE)
# Create data frame for empirical and theoretical p-values
pval_df_qq <- ddply(.data = pval_df,.variables = ~ technology + Comparison + Method,.fun = function(x){
  x <- x[order(x$pVal),]
  x$pVal_theorical[!is.na(x$pVal)] <- (1:(sum(!is.na(x$pVal))))/(sum(!is.na(x$pVal)))
  x$pVal_theorical_rounded[!is.na(x$pVal)] <- round((1:(sum(!is.na(x$pVal))))/(sum(!is.na(x$pVal))),digits = 2)
  x$KS <- ks.test(x = x$pVal_theorical[!is.na(x$pVal)],y = x$pVal[!is.na(x$pVal)])$statistic
  x$KS_pVal <- ks.test(x = x$pVal_theorical[!is.na(x$pVal)],y = x$pVal[!is.na(x$pVal)])$p.value
  #x$KLD <- KLD(x$pVal_theorical[!is.na(x$pVal)],x$pVal[!is.na(x$pVal)])$sum.KLD.px.py
  #x$KLD_0.1 <- KLD(x$pVal_theorical[!is.na(x$pVal) & x$pVal_theorical < 0.1],x$pVal[!is.na(x$pVal) & x$pVal_theorical < 0.1])$sum.KLD.px.py
  return(x)
})
pval_df_KS_summary <- ddply(.data = pval_df_qq,.variables = ~ technology + Comparison + Method,.fun = function(x){
  colMeans(x[,7:8])})
KS_comp <- ddply(pval_df_KS_summary, ~ technology + Comparison, function(x) rank(x[,4]))
colnames(KS_comp) <- c("technology","Comparison",levels(pval_df_KS_summary$Method))
KS_comp_melted <- melt(KS_comp)
KS_summary <- ddply(KS_comp_melted, ~ variable, function(x) mean(x$value))
colnames(KS_summary) <- c("method","value")
saveRDS(object = KS_summary,file = "../data/summary/KS_summary.RDS")
```